On consistency scores in text data with an implementation in R

### 2021-01-07 outputs/documents/paper_ngrams.Rmd
Changed transformer to Transformer

In future work we intend to investigate in more advanced language models such as word embeddings and transformers. We will consider pre-trained word embedding models including Word2Vec [@mikolov2013efficient] [@mikolov2013distributed] and GloVe [@pennington2014glove], which place each word in a multi-dimensional space such that distance between words can illustrate their relationship [@bengio2003neural]. This approach of representing words in vectors has a long history, but the implementation of @bengio2003neural has become the foundation for much subsequent work.

We will also consider incorporating generative pre-trained transformer models such as GPT-2 [@radford2019language], GPT-3 [@brown2020language], and BERT [@devlin2018bert]. These models are based on the transformer architecture [@vaswani2017attention]. Proposed by @vaswani2017attention in 2017, the transformer network architecture for neural networks has been found to outperform both  recurrent neural network-based and convolutional neural network-based models in computational efficiency [@vaswani2017attention]. Since the emergence of the transformer model, most of the representative pre-trained models are built based on this architecture [@hanretty2018comparing].

>>>>

In future work we intend to investigate in more advanced language models such as word embeddings and Transformers. We will consider pre-trained word embedding models including Word2Vec [@mikolov2013efficient] [@mikolov2013distributed] and GloVe [@pennington2014glove], which place each word in a multi-dimensional space such that distance between words can illustrate their relationship [@bengio2003neural]. This approach of representing words in vectors has a long history, but the implementation of @bengio2003neural has become the foundation for much subsequent work.

We will also consider incorporating generative pre-trained Transformer models such as GPT-2 [@radford2019language], GPT-3 [@brown2020language], and BERT [@devlin2018bert]. These models are based on the Transformer architecture [@vaswani2017attention]. Proposed by @vaswani2017attention in 2017, the Transformer network architecture for neural networks has been found to outperform both recurrent neural network-based and convolutional neural network-based models in computational efficiency [@vaswani2017attention]. Since the emergence of the Transformer model, most of the representative pre-trained models are built based on this architecture [@hanretty2018comparing].
